\section{Some Familiar Topological Spaces and Basic Topological Concepts}

\subsection{Exercises 1.2}


\question{Let $A = (0,1) \cup (1,3)$. For the given $x \in A$, give a value of $r > 0$ such that $(x-r, x+r) \subseteq A$.}

\begin{parts}
 
 \part{$x = \frac{3}{4}$}
 \part{$x = 2$}
 \part{$x = \frac{9}{8}$}
 
\begin{solution}
 $\frac{1}{16}$
\end{solution}

\end{parts}

\question{Prove that A = $(0,1) \cup (1,3)$ is an open subset of $\R$.}

\begin{solution}
\\Case 1: $x \in (0,1)$ \\
Let $d = \text{min}\{1-x,x\}$. $(x-\frac{d}{2},x+\frac{d}{2}) \subseteq A$ is an open set. \\
Case 2: $x \in (1,3)$ \\
Let $d = \text{min}\{3-x,x-1\}$. The proof proceeds similarly as Case 1. \\
As $\forall x \in A \exists$ an open interval $\subseteq A$ which contains $x$, $A$ is an open set by definition.
\end{solution}

\question{Prove than an ordinary open interval is an open subset of $\R$ but that an open set need \textit{not} be an open interval.}

\begin{solution}
 \\All open intervals are open subsets: \\
 Replace 0 with $x-r$ and 1 with $x+r$ as in Case 1 from the question above. \\
 Open sets need not be an open interval: \\
 The empty set is an open set, but no open interval is empty, as it contains $x$ (open intervals are in the form $(x-r,x+r)$).
\end{solution}

\question{State precisely what it means when a subset $A$ of $\R$ is \textit{not} open.}

\begin{solution}
 $\exists x \in A$ such that $(x-r,x+r)-A \neq \emptyset \forall r > 0$
\end{solution}

\question{Prove that the following subsets of $\R$ are not open.}

\begin{parts}
 
 \part{The set of rational numbers}
 
 
\begin{solution}
 \\An open interval is nonempty. As it is an open set, it cannot contain a single point only (next question) so it must contain at least 2 points. WLOG, let the 2 points be $p < q$. Using limits, $\exists n \in \N$ such that $r = p + \frac{\sqrt{2}}{n} < q$. Since all open intervals contain an irrational $r$, no open intervals can be a subset of the rationals, hence it is not open.
\end{solution}

 \part{A set consisting of a single point}
 
 
\begin{solution}
 \\$\forall$ open intervals $(x-r,x+r)$, it contains the distinct points $x$ and $x+\frac{r}{2}$. Therefore, $\{x\}$ cannot be open.
\end{solution}

 \part{An interval of the form $[a,b)$, where $a < b$}
 
 
\begin{solution}
\\ $\forall$ open intervals $(a-r,a+r)$, $b=a-\frac{r}{2}$ is a point in that interval which is outside of $[a,b)$.
\end{solution}

 \part{The set $A = \{x\in\R:x\neq\frac{1}{n},\text{ for }n\in\mathbb{Z}^+\}$}
 
 
\begin{solution}
\\ $\frac{1}{n}$ tends to 0. Therefore $\forall r > 0 \exists n \in \N$ such that $r > \frac{1}{n}$. Therefore all open intervals $(0-r,0+r)$ contains a point outside of $A$.
\end{solution}
\end{parts}

\subsection{Theorem 1.3}

\question

\begin{parts}
 
 \part{The union of any collection of open subsets of the real line is also an open subset of the line}
 
 
\begin{solution}
 \\ Let $\bigcup A$ denote the union of subsets $A$. Then
$$x \in \bigcup A \Rightarrow x \in A \Rightarrow x \in (x-r,x+r) \subseteq A \subseteq \bigcup A$$
for some $r > 0$. \\
As all points in $\bigcup A$ are in open intervals which are subsets of $\bigcup A$, the union is open by definition.
\end{solution}

\part{The intersection of any finite collection of open subsets of the real line is also an open subset of the line.}

\begin{solution}
 \\This can be proven with induction. \\
Let $A$ and $B$ be open sets. $x \in A \cap B \Rightarrow x \in A$. Since $A$ is open, $\exists r_A > 0$ such that
$$x \in (x-r_A,x+r_A) \subseteq A$$
The same holds for $B$. Letting $r = \text{min}\{r_A,r_B\}$,
$$x \in (x-r,x+r) \subseteq A \cap B \forall x \in A \cap B$$
The same proof is used for the base case and the induction step.
\end{solution}

\part{Both the empty set and $\R$ itself are open subsets of the real line.}

\begin{solution}
 \\Empty set: \\
 $$a \Rightarrow b$$
 is defined to be true when $a$ is false. The definition of an open set $A$ involves the assumption $x \in A$, which is false, so it is vacuously true for the empty set. \\
 $\R$: \\
 $\forall x \in \R, (x-1,x+1) \in \R$
\end{solution}

\end{parts}

\subsection{Exercise 1.4}

\question{Give an example of an infinite collection of open subsets of the real line whose intersection is not open, thus showing that the finiteness condition in Theorem 1.3(b) is necessary.}

\begin{solution}
 $$\bigcap A \text{ where } A = \{(-r,r)|r>0\}$$
 Obviously $0 \in (-r,r) \forall r > 0$. However, the intersection does not contain any nonzero element, because $\forall x \neq 0$,
 $$x \notin \{-\frac{|x|}{2},\frac{|x|}{2}\}$$
 The open intervals that form the intersection are open sets, but the intersection contains only 1 element, so it is not open.
\end{solution}

\subsection{Theorem 1.6}

\question

\begin{parts}
 
 \part{The intersection of any collection of closed sets is closed.}
 
 
\begin{solution}
 \\Let $C_i$ be a closed set, and the corresponding open set be defined as $O_i = \R - C_i$.
 
 $$\bigcap_{i \in I} C_i = \bigcap_{i \in I} \R - O_i = R - \bigcup_{i \in I} O_i$$
 
 $\bigcup_{i\in I}O_i$ is a union of open sets, so it is open. Hence its complement (intersection of closed sets) is closed.
\end{solution}

\part{The union of any finite collection of closed sets is closed.}

\begin{solution}
 
 $$\bigcup_{n \in \N} C_n =  \bigcup_{n \in \N} \R - O_n = R - \bigcap_{n \in \N} O_n$$
 
 And the proof follows similar to the case above.
\end{solution}

\part{$\emptyset$ and $\R$ itself are both closed}

\begin{solution}
 Their complements are each other, which are open.
\end{solution}
\end{parts}

\subsection{Exercise 1.7}

\question{State precisely what it means when a subset of $\R$ is not closed. (Do this in term of points; saying that a set is not closed if its complement is not open is true, but is not what we want here.}

\begin{solution}
 \\Let that subset be $A$. It is not closed when there is a point outside of it whose every open interval intersects with $A$.
 
 $$\exists x \in \R - A \text{ such that } (x-r,x+r) \cap A \neq \emptyset \forall r > 0$$
\end{solution}

\question{Which of the following subsets of $\R$ are closed? Which are open?}

\begin{parts}
 
 \part{The set $\mathbb{Z}$ of integers.}
 \part{The set of rational numbers.}
 \part{A set consisting of a single point.}
 \part{An interval of the form $[a,b)$, where $a < b$.}
 \part{The set $A = \{x\in\R: x \neq \frac{1}{n} \text{ for } n \in \mathbb{Z}^+\}$.}
 \part{The set $A = \{x\in\R: x \neq \frac{1}{n} \text{ for } n \in \mathbb{Z}^+ \text{ and } x \neq 0\}$.}
 
 
\begin{solution}
 \\Closed: a, c \\
 Open: f
\end{solution}

\end{parts}

\question{Prove that an ordinary closed interval is a closed subset of $\R$, but a closed set need not be a closed interval.}

\begin{solution}
 \\Let the closed interval be $[a,b]$, where $a < b$. We want to prove that its complement is open. Let $x < a$ be in its complement. Then
 $$(x-r,x+r) \text{ where } r = \frac{a-x}{2}$$
 is an open interval in its complement. A similar open interval can be deduced for $x > b$. Therefore, the complement is open, and the closed interval is closed. \\
 For the second part of the question, note that $\R$ is closed, but is not a closed interval. (Or else, let $\R = [a,b]$, and $\R-[a,b] \neq \emptyset$ forms a contradiction.)
\end{solution}

\question{Give an example of an infinite collection of closed subsets of whose union is not closed, thus showing tht the finiteness condition in theorem 1.6(b) is not necessary.}

\begin{solution}
 \\Let the collection be
 $$A = \{[-r,r]|0<r<1\}$$
 It is obvious that $\bigcup A = (-1,1)$. The complement of $(-1,1)$ contains 1, whose every open interval intersects with $(-1,1)$. Hence the complement is not open, so $\bigcup A$ is not closed.
\end{solution}

\subsection{Exercise 2.3}

\question{Show that the absolute value formula, $d(x,y) = |x-y|$ is indeed a metric on the real line. Describe the \textbf{1-ball} centered at 0 in the topology induced by this metric.}

\begin{solution}
Trivial.
\begin{enumerate}
 \item $|x-y| \geq 0 \forall \{x,y\} \subset \R$ \\
 \item $|x-y| = 0$ iff $x=y$ \\
 \item $|x-z|+|y-z|=|x-z|+|z-y| \geq |x-z+z-y| = |x-y|$ \\
 \end{enumerate}
 
 The 1-ball is ordinary closed interval $(-1,1)$.
\end{solution}

\question{Show that the distance formula is a metric on the Euclidean plane. Describe the 1-ball centered at $(0,0)$ in the topology induced by this metric.}

\begin{solution}
 \\In fact, this can be proven for all finite Euclidean spaces $\R^n$, where
 $$d(x,y) = \sqrt{\sum_{i=1}^n (x_i-y_i)^2}$$
 $d(x,y) \geq 0 \forall \{x,y\} \subset \R^n, d(x,y) = 0 \text{ iff } x = y, d(x,y) = d(y,x) \forall \{x,y\} \subset \R^n$ are all trivial. What remains is the triangle inequality.
 Let $a_i = x_i - z_i$ and $b_i = z_i - y_i$. Therefore $a_i + b_i = x_i - y_i$.
 
 
\begin{align*}
 d(x,z) + d(y,z) &= \sqrt{\sum_i a_i^2} + \sqrt{\sum_i b_i^2} \\
 (d(x,z) + d(y,z))^2 &= \sum_i(a_i^2 + b_i^2) + 2\sqrt{\left(\sum_i a_i^2\right)\left(\sum_i b_i^2\right)} \\
 (d(x,z)+d(y,z))^2 - (d(x,y))^2 &= 2\left(\sqrt{\left(\sum_i a_i^2\right)\left(\sum_i b_i^2\right)} - \sum_i a_i b_i\right) \\
\end{align*}
This is greater than 0 (from the Cauchy-Schwarz Inequality). Rearranging and taking the square root of both sides (we can do this because the distance formula is always positive) yields the desired inequality. \\
The 1-ball is the open disk with a radius of 1.
\end{solution}

\question{Define the obvious metric for Euclidean 3-space, $E^3 = \R \times \R \times \R = \{(x,y,z):x,y,z \in \R\}$. Describe the 1-ball centered at the point $(0,0,0)$ in the topology induced by this metric. (In this topology, an $r$ ball really is a ball - hence the name "$r$-ball.")}

\begin{solution}
 The metric is defined in the question above, and the 1-ball is an open sphere with a radius of 1.
\end{solution}

\question{Show that for any metric space $(X,d)$,}

\begin{parts}
 
 \part{The union of any collection of open sets is open.}
 
 
\begin{solution}
 \\Let $O_i$ be open. Then
 $$x \in \bigcup_i O_i \Rightarrow x \in O_i \Rightarrow x \in S_r(x) \subseteq O_i$$
 Since $O_i \subseteq \bigcup O_i$, we have
 $$x \in \bigcup_i O_i \Rightarrow x \in S_r(x) \subseteq \bigcup_i O_i$$
\end{solution}

\part{The intersection of any finite collection of open sets is open.}

\begin{solution}
 \\Similar to the metric case, this can be proven using induction. \\
Let $A$ and $B$ be open sets.
$$x \in A \cap B \Rightarrow x \in A \Rightarrow x \in S_{r_A}(x) \subseteq A$$
Similarly,
$$x \in S_{r_B}(x) \subseteq B$$
Letting $r = \text{min}\{r_A,r_B\}$, we have
$$x \in A \cap B \Rightarrow x \in S_r(x) \subseteq A \cap B$$
\end{solution}

\part{The empty set and $X$ itself are open.}

\begin{solution}
 \\The fact that the empty set is open is vacuously true, and the definition of $S_r(x)$ implies $S_r(x) \subseteq X$, so $X$ is also open.
\end{solution}
\end{parts}

\question{A set can have more than one metric defined on it, and different metrics may give rise to different topologies.}

\begin{parts}
 
 \part{Let $X = \R$ and define a metric on $X$ by $d(x,y) = 1$ if $x \neq y$, $d(x,y) = 0$ if $x = y$. Prove that $d$ is a metric on $X$. What is $S_\frac{1}{2}(0)$ in this metric? Is $(X,d)$ the same space as $\R$ with its usual metric topology? In other words, does this metric give rise to the same topology on $\R$ as the usual metric does?}
 
 
\begin{solution}
 \\The fact that $d$ is a metric is trivial. $S_\frac{1}{2}(0) = \{0\}$. This metric gives rise to a different topology, as $\{0\}$ is open in this topology, but not the usual topology.
\end{solution}

\part{Let $X$ be the Euclidean place and define a metric on $X$ by $d((x_1,x_2),(y_1,y_2)) = |x_1-y_1| + |x_2 - y_2|$. Prove that $d$ is a metric on the plane, and describe the $r$-balls in this metric. Does this metric give rise to the same topology as the usual metric on this plane?}

\begin{solution}
 \\ $d(x,y) \geq 0 \forall \{x,y\} \subset \R^n, d(x,y) = 0 \text{ iff } x = y, d(x,y) = d(y,x) \forall \{x,y\} \subset \R^n$ are all trivial. What remains is the triangle inequality.

\begin{align*}
 d(x,z) + d(y,z) &= |x_1 - z_1| + |x_2 - z_2| + |y_1 - z_1| + |y_2 - z_2| \\
 &= |x_1 - z_1| + |z_1 - y_1| + |x_2 - z_2| + |z_2 - y_2| \\
 &> |x_1 - y_1| + |x_2 - y_2| \\
 &= d(x,y) \\
\end{align*}
The r-balls of $x$ are open squares centered at $x$ with sides of length $r$. It is obvious that all open disks $D$ centered at $x$ contain open squares $S$ also centered at $x$, (such that $x \in S \subset D$) and vice versa. If $A$ is an open set under the usual topology, then
$$x \in A \Rightarrow x \in D$$
Combining this with
$$x \in S \subset D$$
we have
$$x \in A \Rightarrow x \in S$$
so $A$ is an open set under this metric. Similarly, if $B$ is an open set under this metric, $B$ is also an open set under the usual metric. Therefore, both topologies are the same.
\end{solution}
\end{parts}

\subsection{Exercise 3.3}

\question{Let $(\mathbb{Q},d)$ be the space of rational numbers with the metric topology induced by the absolute value metric $d$.}

\begin{parts}
 
 \part{Show that the set $\{y \in \mathbb{Q}:1 < y < 2\}$ is open in $(\mathbb{Q},d)$.}
 
 
\begin{solution}
 \\Denote the set as $A$. Let $r =$ min$\{\frac{2-y}{2},\frac{y-1}{2}\}$. Then
 $$y \in (y-r,y+r) \cap A \subseteq A \forall y \in A$$
\end{solution}

\part{Show that the set $[\sqrt{2},\sqrt{3}]\cap \mathbb{Q}$ is open in $(\mathbb{Q},d)$.}

\begin{solution}
 Noting that both $\sqrt{2}$ and $\sqrt{3}$ are not in the set, the proof can be obtained by replacing the rationals 1 and 2 in the solution above.
\end{solution}
\end{parts}

\question{Let $S$ = [1,2] be given teh topology induced by the absolute value metric. Show that $[1,\frac{3}{2}),(\frac{3}{2},2]$ and $[1,2]$ are all open in $(S,d)$.}

\begin{solution}
 \\For the first set, if $x \neq 1$, let $r =$ min$\{\frac{3}{2}-x,x-1\}$. Then $S_r(x) \cap [1,\frac{3}{2}) = S_r(x)$, and so
 $$x \in [1,\frac{3}{2}) \Rightarrow x \in S_r(x) \subset [1,\frac{3}{2})$$
 If $x = 1$, then $r = \frac{5}{4}$ suffices. \\
 A similar approach is used for the second and third set, noting the special cases for $x=1$ and $x=2$.
\end{solution}

\question{Let $(\mathbb{Z},d)$ be the space of integers with the metric topology induced by the absolute value metric. Show that \textit{every} subset of $\mathbb{Z}$ is open in $(\mathbb{Z},d)$. In particular, any set consisting of a single point is open in $(\mathbb{Z},d)$.}

\begin{solution}
 \\Let $A$ be a subset, and let $r = \frac{1}{2}$. Then $\forall x \in A$,
 $$x \in S_r(x) \cap A = \{x\} \subseteq A$$
\end{solution}

\question{Let $(X,d)$ be a discrete space. Show that every subset of $X$ is open in $(X,d)$.}

\begin{solution}
 \\Let $A$ be a subset. Then
 $$A = \bigcup\{\{x\}|x \in A\}$$
 which is the union of open sets, so $A$ is also open.
\end{solution}

\subsection{Theorem 4.1}

\question{A subset $A$ or $\R$ is open in the metric topology induced by the absolute value metric if and only if for each point $x \in A$, there exist real numbers $a$ and $b$ with $a < x < b$, such that $x \in (a,b) \subseteq A$.}

\begin{solution}
 \\$\Leftarrow$: \\
 Let $r =$ min$\{x-a,b-x\}$. Then $\forall x \in A$,
 $$x \in (x-r,x+r) \subseteq (a,b) \subseteq A$$
 $\Rightarrow$: \\
 As $A$ is open,
 $$x \in A \Rightarrow x \in S_r(x)$$
 so $a = x - r$ and $b = x + r$ suffices.
\end{solution}

\subsection{Exercise 4.3}

\question{Convince yourself that the real line is a totally ordered set. Give an example of a set with an order relation that satisfies (1), (2), and (3) of Definition 4.2, but does \textit{not} satisfy (4). Such an ordered set is called \textbf{partially ordered} since not every pair of elements can be compared. [\textit{Hint}: Consider $\mathcal{P}(X)$ with "$\leq$" thought as "subset of].}

\begin{solution}
 \\Intuitively, real numbers satisfy (1) through (4). A rigorous proof involves Dedekind cuts, which is (probably) out of the scope of this book. \\
 $\subseteq$ in $\mathcal{P}(X)$ is one such example. (1) and (3) are trivial, and (2) is true by definition. However, $\{1,2\}$ and $\{3,4\}$ are elements of $\mathcal{P}(\N)$ where both elements cannot be compared.
\end{solution}

\subsection{Exercise 4.5}

\question{Every open subset of $\R$ has cardinality $c$}

\begin{solution}
\\Let $A$ be an open subset. $\forall x \in A$,
$$x \in (x-r,x+r) \subseteq A$$
The function
$$f(y) = \frac{y-x}{r} \times \frac{\pi}{2}$$
is a bijection from $(x-r,x+r)$ to $\R$, so they share the same cardinality $c$. As
$$(x-r,x+r) \subseteq A \subseteq \R$$
$|A| = c$ by the Cantor-Bernstein Theorem.
\end{solution}

\question{For any positive integer $n$, there are open subsets of $[0,\Omega)$ with cardinality $n$. In particular, there are points $x$ in $[0,\Omega)$ such that the singleton set $\{x\}$ is an open set. But $[0,\Omega)$ is not discrete - not every singleton set is open.}

\begin{solution}
 \\$[1,n]$ is a set with cardinality $n$. To show that it is open, $\forall x \in [1,n]$,
 $$0 < x < n+1 \text{ such that } x \in (0,n+1) \subseteq A$$
 Putting $n=1$ gives us a singleton set that is open. However, not all singleton sets are open, e.g. $\{\omega\}$. For it to be open, $a < \omega < b$ such that
 $$\omega \in (a,b) \subseteq \{\omega\}$$
 Since $\omega$ is a limit ordinal, $a < a+1 < \omega < b$, so
 $$a + 1 \in (a,b) - \{\omega\}$$
 which is a contradiction.
 \end{solution}

\question{There are open subsets of $[0,\Omega)$ of cardinality $\aleph_0$ and there are open subsets of $[0,\Omega)$ of cardinality $\aleph_1$.}

\begin{solution}
 \\$\forall n \in \N$, $[n+1,\omega)$ is a subset of cardinality $\aleph_0$. To show that it is open, $\forall x \in [n+1,\omega)$,
 $$n < x < \omega \text{ such that } x \in (n,\omega) \subseteq [n+1,\omega)$$
 Similarly, $[n+1,\Omega)$ is a subset of cardinality $\aleph_1$. The bijective function from $[0,\Omega)$ to $[n+1,\Omega)$ is given by
 $$f(x) = \begin{cases} x + n + 1 & x \in \N \\ x & \text{else} \end{cases}$$
 To show that it is open, $\forall x \in [n+1,\Omega)$,
 $$n < x < \Omega \text{ such that } x \in (n,\Omega) \subseteq [n+1,\Omega)$$
\end{solution}

\question{Supplementary: No countable collection of subsets of $[0,\Omega]$ intersect at $\{\Omega\}$ only.}

\begin{solution}
 \\Let $A_n$ be an open set in the collection. Since $\Omega \in A$,
 $$\Omega \in (a_n,\Omega] \subseteq A$$
 Where $(a_n,\Omega] = [a_n+1,\Omega]$. Let $b_n = a_n+1$, and consider
 $$b = \bigcup_{n \in \N} b_n$$
 The union of ordinals (b) is an ordinal that is greater than all of the ordinals in the union $(b > b_n)$. \\
 Since we have subsets of $A_n$,
 $$\bigcap_{n \in \N} [b_n,\Omega] \subseteq \bigcap_{n \in \N} A_n$$
 Since $b > b_n \forall n \in \N$, $b$ is an element of the set in the left, meaning the countable ordinal $b$ is an element of the intersection, which is a contradiction.
\end{solution}

\subsection{Exercise 4.6}

\question{Show that $\omega = [0,\omega)$ with the order topology is a discrete space, so is the same as $\mathbb{Z}^+\cap\{0\}$ when given the metric topology induced by the absolute value metric on $\R$.}

\begin{solution}
 \\First we prove that all singleton sets $\{x\}$ are open.
 $$x = 0 \Rightarrow x \in [0,1) \subseteq \{0\}$$
 $$x \neq 0 \Rightarrow x \in (x-1,x+1) \subseteq \{x\}$$
 Note that $x-1$ exists $\forall x \neq 0$, as $x$ is a nonzero natural number. \\
 Since
 $$\omega = \mathbb{Z}^+ \cup \{0\}$$
 and both are discrete, they are the same.
\end{solution}

\question{The definition of the order topology is given in terms of open intervals. Let $(X, \leq)$ be a totally ordered set and give it the order topology. Show that a subset of $x$ is open in the order topology if and only if it is a union of open intervals. Because of this, we say that the collection of open intervals is a \textit{basis} for the order topology on a totally ordered set.}

\begin{solution}
 \\Let $A$ be an open subset. Since $A$ is open, $\forall x \in A$,
 $$x \in O_x \subseteq A$$
 where $O_x$ denotes an open interval containing $x$ that is a subset of $A$. Then
 $$A = \bigcup_{x \in A} O_x$$
 So all open sets are unions of open intervals $O_x$. Since open intervals are open sets (this can easily be observed), any union of open intervals are open sets.
\end{solution}

\subsection{Exercise 5.3}

\question{State precisely what it means when a sequence in $(X,d)$ does not converge to the point $x \in X$.}

\begin{solution}
 $\forall N \in \N > 0, r > 0, \exists r > 0, n > N$ such that $x_n \notin S_r(x)$
\end{solution}

\question{Let $\{x_n:n\in\mathbb{Z}^+\}$ be the sequence in $\R$ defined by $x_n = \frac{1}{n}$. Does this sequence converge? To what? Prove it.}

\begin{solution}
 \\It converges to 0. We take for granted that natural numbers are unbounded above, i.e. $\forall r \in \R \exists n \in \N$ such that $n > r$. Then $\forall r > 0$,
 $\exists N \in \N > \frac{1}{r}$, so $r > x_n \forall n \in \N > N$, which is equivalent to $x_n \in S_r(0) \forall n \in \N > N$.
\end{solution}

\question{Let $\{x_n:n\in\mathbb{Z}^+\}$ be the sequence in $\R$ defined by $x_n = (-1)^n(\frac{1}{n})$. Does this sequence converge? To what? Prove it.}

\begin{solution}
It converges to 0. Note that $|x_n| \in S_r(0) \Rightarrow x_n \in S_r(0)$. Since $|x_n|$ converges by the previous question, so does $x_n$.
\end{solution}

\question{Let $\{x_n:n\in\mathbb{Z}^+\}$ be the sequence in $\R$ defined by $x_n = (-1)^n$. Does this sequence converge? To what? Prove it.} \label{alternatingsign}

\begin{solution}
 \\It does not converge to $a \forall a \in \R$. \\
 If $a > 1$, let $r = a - 1$, then $x_n$ never enters $S_r(a)$. \\
 If $a < -1$, let $r = -1-a$, then $x_n$ never enters $S_r(a)$. \\
 If $a = 1$ or $a = -1$, let $r = 1$, then $x_n$ never enters $S_r(a)$. \\
 Else, let $r = \text{ min} \{1-a,a+1\}$, then $x_n$ never enters $S_r(a)$.
\end{solution}

\subsection{Theorem 5.4}

\question{A sequence in a metric space can converge to at most one point.}

\begin{solution}
 \\Proof by contradiction. Let it converge to two distinct points $a$ and $b$. Let $r = \frac{d(a,b)}{2}$, so $S_r(a)$ and $S_r(b)$ are disjoint by the triangle inequality.\\
 Since the sequence converges to both points, $\exists \{N_a,N_b\} \subseteq \N$ such that
 $$n \in \N > N_a \Rightarrow x_n \in S_r(a)$$
 and similarly for $b$. \\
 Let $N = \text{ max} \{N_a,N_b\}$. Then $x_{N+1} \in S_r(a)$ and $x_{N+1} \in S_r(b)$ which is a contradiction.
\end{solution}

\subsection{Theorem 5.5} \label{thm3.5.5}

\question{A subset $S$ of a metric space $X$ is closed if and only if whenever a sequence of point of $S$ converges to a point $x \in X$, then $x \in S$.}

\begin{solution}
 \\$\Rightarrow$: \\
 Assume the opposite. Then $x \in X-S$ but $S_r(x)$ intersects with $S$ $\forall r > 0$. Then $X-S$ is not open (it has no open subset containing $x$), so $S$ is not closed, which is a contradiction. \\
 $\Leftarrow$: \\
 Assume the opposite. Then $X-S$ is not open, so $\exists x \in X-S$ such that $S_r(x)$ intersects with $S$ $\forall r > 0$. Let $y_n \in S_{\frac{1}{n}}(x) \cap S$. Then $y$ is a sequence in $S$ that tends to a point $x$ outside of $S$. This is a contradiction.
\end{solution}

\subsection{Exercise 5.6}

\question{Use Theorem 5.5 to decide if the following subsets of the real line are closed (in the metric topology induced by the absolute value metric).}

\begin{parts}
 
 \part{$[0,1]$}
 \part{$[1,\infty)$}
 \part{$\{x\in\R:x=\frac{1}{n} \text{ for }n \in \mathbb{Z}^+\}$}
  \part{$\{x\in\R:x=\frac{1}{n} \text{ for }n \in \mathbb{Z}^+\text{, or }x=0\}$}
  \part{$\{x\in\R:x=\frac{1}{\sqrt{n}} \text{ for } n \in \mathbb{Z}^+\}$}
  
\end{parts}

\begin{solution}
 Closed, closed, not closed, closed, not closed.
\end{solution}

\question{Is$(\R-\Q)\cap\{x\in\R:x=\frac{1}{\sqrt{n}} \text{ for } n \in \mathbb{Z}^+\}$ a closed subset of the \textit{irrationals} with the metric topology induced by the absolute value metric?}

\begin{solution}
 \\Yes. Whenever the sequence tends to an irrational point $x$, $x$ is in the set. Proof by contradiction: \\
 If $x < 0$, let $r = -x$. The sequence never enters $S_r(x)$, so it cannot converge to $x$. \\
 $If x > 1$, let $r = x-1$. The sequence never enters $S_r(x)$, so it cannot converge to $x$. \\
If $0<x<1$, then $\frac{1}{\sqrt{n+1}} < x < \frac{1}{\sqrt{n}}$. Let $r = \text{ min} \{x-\frac{1}{\sqrt{n+1}}, \frac{1}{\sqrt{n}}-x\}$. The sequence never enters $S_r(x)$, so it cannot converge to $x$. \\
In all other cases, $x$ is either rational or in the subset itself.
\end{solution}

\question{Let $[p_n = (x_n,y_n):n \in \mathbb{Z}^+\}$ be a sequence in $E^2$, the Euclidean plane. Prove that $p_n \rightarrow p = (x,y)$ if and only if both $x_n \rightarrow x$ and $y_n \rightarrow y$. (Thus a sequence in the plane converges if and only if it converges "coordinate-wise")}

\begin{solution}
 \\$\Rightarrow$: \\
 Obviously, $d(p_n,p) \geq d(x_n,x)$, similarly for $y$. Hence $p_n \in S_r(p) \Rightarrow x_n \in S_r(x)$ and similarly for $y$. Since $p_n$ converges to $p$, $x_n$ converges to $x$ and so does $y$. \\
 $\Leftarrow$: \\
 $\forall r > 0$, let $r' = \frac{r}{\sqrt{2}}$. Then $\exists N_x \in \N$ such that $n \in \N > N_x \Rightarrow x_n \in S_{r'}(x)$. A similar $N_y$ exists for $y$. Letting $N = \text{ max}\{N_x,N_y\}$ implies that $\forall n > N$, $p_n \in S_r(p)$. As this holds $\forall r > 0$, we can conclude that $p_n \rightarrow p$.
\end{solution}

\question{Prove that every real number can be written as the limit of a convergent sequence of \textit{rational} numbers, i.e., if $r \in \R$, exhibit a sequence $\{x_n:n\in\mathbb{Z}^+\} \subseteq \Q$ such that $x_n \rightarrow r$.}

\begin{solution}
 This can be done by extending the decimal expansion of said real number, e.g.
 $$\pi = 3,3.1,3.14,3.141,\dots$$
 The maximum error decreases by one-tenth every term, so this sequence converges to the real number.
\end{solution}

\question{A real number $r$ is called the \textbf{least upper bound} or \textbf{supremum} of a set $S \subseteq \R$ if

\begin{parts}
 
 \part{$r \geq s$ for all $s \in S$, and}
 \part{If $t \in \R$ is a real number such that $t \geq s$ for all $s \in S$, then $t \geq r$.}
 
\end{parts}

The least upper bound of a set $S$ is denoted by sup $S$. Prove that if $S \subseteq \R$ and sup $S$ exists, then there exists a sequence of points of $S$ that converges to sup $S$.}

\begin{solution}
 \\Denote a sequence with $r_0 = 1, r_{i+1} = \frac{r_i}{2}$. Let $s$ denote the upper bound. Since $s - r_i$ is not the upper bound, $\exists s_i \in S$ where $s - r_i < s_i \leq s$. Then $s_i \in S_{r_i}(s)$. We now show that $s_i$ tends to $s$. \\
 Since $r_i$ obviously tends to 0, $\exists r_i < r \forall r > 0$, then $s_i \in S_{r_i}(s) \subseteq S_r(s)$. Therefore there is a sequence in $S$ that converges to its supremum. This is probably the intended solution of the question above.
\end{solution}

\question{Prove that if $S \subseteq \R$ and sup $S$ exists, then if $S$ is closed, sup $S \in S$. Is the converse true?}

\begin{solution}
\\ There is a sequence in $S$ that tends to sup $S$. Since $S$ is closed, this implies sup $S \in S$ by \hyperref[thm3.5.5]{Theorem 5.5}. \\
The converse is not true, because $(0,1]$ is not closed.
\end{solution}

\subsection{Exercise 5.8}

\question{If a sequence converges to a point $x$, then $x$ is an accumulation point of the sequence. (So "ultimately" implies "frequently.")}

\begin{solution}
 \\This follows from the definition. Since the sequence converges to $x$, $\forall r > 0$,
 $$\exists N' \in \N \text{ such that } n \in \N > N' \Rightarrow x_n \in S_r(x)$$
Letting $n =$ max$\{N'+1,N\}$, we have $x_n \in S_r(x)$ for arbitrary $r$ and $N$.
\end{solution}

\question{If $x$ is an accumulation point of a sequence, the sequence need not converge to $x$. (So "frequently" does not imply "ultimately".)}

\begin{solution}
 \\Let $x_n = (-1)^n$. Then 1 is an accumulation point, because for arbitrary $r$ and $N$, we know $2N \geq N$ so that
 $$x_{2N} = 1 \in S_r(1) \forall r > 0$$
 However, the sequence does not converge to 1. \hyperref[alternatingsign]{see this problem}
\end{solution}

\question{A subset $F$ of a metric space $X$ is closed if and only if whenever $x \in X$ is an accumulation point of a sequence of points of $F$, then $x \in F$.}

\begin{solution}
 \\$\Rightarrow$: \\
 Let $r_0 = 1$ and $r_{i+1} = \frac{r_i}{2}$. Define $x_0$ to be the first point in the sequence in $F$ to be in $S_{r_0}(x)$. Define $x_{i+1}$ to be the first point after $x_i$ in the sequence to be in $S_{r_{i+1}}(x)$. Then $x_n$ tends to $x$, as 
 $$\forall r > 0 \exists r_i < r \text{ such that } \forall n > i, x_n \in S_{r_i}(x) \subseteq S_r(x)$$
 Since $F$ is closed and $x_n$ is a sequence in $F$, we can conclude that $x \in F$ by \hyperref[thm3.5.5]{Theorem 5.5}. \\
 
 $\Leftarrow$: \\
 For all sequences in $F$ that converge to $x$, $x$ is an accumulation point, so $x \in F$. This implies $F$ is closed by \hyperref[thm3.5.5]{Theorem 5.5}.
\end{solution}

\question{State precisely what it means when the point $x \in X$ is \textit{not} an accumulation point of the sequence $\{x_n:n\in\mathbb{Z}^+\} \subseteq X$.}

\begin{solution}
 $\exists r \in \R > 0, N \in \N$ such that $n \geq N \Rightarrow x_n \notin S_r(x)$
\end{solution}

\subsection{Exercise 6.2}

\question{State precisely what it means when a function $f$ is \textit{not} continuous at a point $x_0$ in its domain.}

\begin{solution}
 $\exists \epsilon > 0$ where $\forall \delta > 0, \exists x \in S_\delta(x_0)$ such that $f(x) \notin S_\epsilon(f(x_0))$
\end{solution}

\question{Prove that the function defined by $$f(x) = \begin{cases} 1 & \text{if } x \geq 2 \\ -1 & \text{if } x < 2 \end{cases}$$ is not continuous at $x=2$, but is continuous everywhere else.}

\begin{solution}
 \\If $x\neq2$, setting $\delta = |x-2|$ suffices. \\
 If $x=2$, then for $\epsilon = 1$, $\forall \delta > 0$,
 $$x + \frac{\delta}{2} \in S_\delta(x) \text{ but } f\left(x + \frac{\delta}{2}\right) = -1 \notin S_1(1)$$
\end{solution}

\question{Prove that the function $g$ defined by $g(x) = \frac{1}{x}$ for $x \in \R$ and $x > 0$ is continuous on its domain.}

\begin{solution}
 \\We want to show that $g(x)$ is continuous at an arbitrary point $c$. In other words, $\forall \epsilon > 0, \exists \delta > 0$ such that $|x-c| < \delta \Rightarrow |f(x)-f(c)| < \epsilon$
 
\begin{align*}
 |f(x)-f(c)| &< \epsilon \\
 \left|\frac{1}{x} - \frac{1}{c}\right| &< \epsilon \\
 \frac{|x-c|}{cx} &< \epsilon \\
 |x-c| &< cx\epsilon \\
\end{align*}

Now we can impose a limit for $\delta$, where $\delta \leq \frac{c}{2}$, so that $\frac{c}{2} \leq x \leq \frac{3c}{2}$. Substituting this into the inequality above yields
$$|x-c| < \frac{c^2}{2} \epsilon$$
Therefore, if we let $\delta =$ min$\{\frac{c^2}{2}\epsilon,\frac{c}{2}\}$, then
$$|x-c| < \delta \Rightarrow |x-c| < \frac{c^2}{2} \epsilon \Rightarrow |x-c| < cx\epsilon \Rightarrow \frac{|x-c|}{cx} < \epsilon \Rightarrow \left|\frac{1}{x} - \frac{1}{c}\right| < \epsilon$$
which completes the proof.
\end{solution}

\subsection{Theorem 6.4} \label{thm3.6.4}

\question{Let $(X,d_1)$ and $(Y,d_2)$ be two metric spaces and let $f:D \subseteq X \rightarrow Y$. The $f$ is \textbf{continuous at} point $x_0 \in D$ if and only if whenever $\{x_n:n\in\mathbb{Z}^+\}$ is a sequence in $D$ that converges to $x_0$, then the sequence $\{f(x_n):n\in\mathbb{Z}^+\}$ converges to $f(x_0)$ in $Y$.}

\begin{solution}
 \\$\Rightarrow$: \\
Since $f$ is continuous, $\forall \epsilon > 0$, $\exists \delta > 0$ such that $f(S_\delta(x_0)) \subseteq S_\epsilon(f(x_0))$. Since $x_n$ converges to $x_0$, $\exists N \in \N$ such that $n \in \N > N \Rightarrow x_n \in S_\delta(x_0)$. This also means that $f(x_n) \in S_\epsilon(f(x_0))$. Therefore
$$\forall \epsilon > 0 \exists N \in \N\text{ such that } n \in \N > N \Rightarrow f(x_n) \in S_\epsilon(f(x_0))$$
so that $f(x_n)$ tends to $f(x_0)$. \\
$\Leftarrow$: \\
Assume $f$ is not continuous. Then $\exists x_0 \in X$ where $f$ is not continuous. That means $\exists \epsilon > 0$ where $\forall \delta > 0, A(\delta_i) = f(S_{\delta_i}(x_0)) - S_\epsilon(x) \neq \emptyset$. Since the set is nonempty, $\exists x_i \in A(\delta_i)$. Now let $\delta_i = 2^{-i}$. Then the sequence $x_i$ tends to $x_0$, but $f(x_i)$ does not tend to $f(x_0)$, as it never enters $S_\epsilon(f(x_0))$. This is a contradiction, so $f$ must be continuous.
\end{solution}

\subsection{Exercise 6.5}

\question{Let $S$ be a sequence in $\R$, and let $\mathbb{Z}^+$ have the discrete topology that it gets by saying that every point in $\mathbb{Z}^+$ is open. Prove that $S$ is continuous.}

\begin{solution}
 Set $\delta = 0.5$. Then $S_\delta(x) = \{x\}$, so $f(S_\delta(x)) = \{f(x)\} \in S_\epsilon(f(x)) \forall \epsilon > 0$
\end{solution}

\question{Let $p$ be a point, and let $Y = \{p\}$. Make $Y$ into a topological space by declaring that the sets $\emptyset$ and $Y = \{p\}$ are open. Let $f:\R \rightarrow Y$ be defined by $f(x) = p$ for all $x \in \R$. Prove that $f$ is continuous. This is a special case of a theorem that says that any constant function is continuous.}

\begin{solution}
 \\(Note: we have not defined convergence in this case where there is no metric) \\
 For any sequence $x_n$ that converges to $x$, it is obvious that $f(x_n)$ is always $p$. Therefore, whenever $x_n$ is a sequence in $\R$ that converges to $x \in \R$, $f(x_n)$ is a (constant) sequence that converges to $f(x) = p$. By \hyperref[thm3.6.4]{Theorem 6.4}, $f$ is continuous.
\end{solution}

\question{Let $f: \R \rightarrow \R$ be defined by $$f(x) = \begin{cases} 1 & \text{if } x \text{ is rational} \\ -1 & \text{if } x \text{ is irrational} \end{cases}$$ Prove that $f$ is not continuous on $\R$. Is $f$ continuous at any point of $\R$?}

\begin{solution}
 \\$f$ is not continuous at any point of $\R$ (hence it is not continuous). \\
 Let $\epsilon = 1$. We take for granted that between any two numbers, one can always find a rational number and an irrational number. This implies $\forall \delta > 0$, $S_\delta(x)$ contains both rational and irrational $x$. Therefore $f(S_\delta(x))$ contains both 1 and $-1$, and so it is not contained in $S_{0.5}(f(x)) \forall x \in \R$.
\end{solution}

\question{Let $f:\R^+ \rightarrow \R$ be defined by $$f(x) = \begin{cases} \frac{1}{q} & \text{if } x = \frac{p}{q} \text{ in lowest terms} \\ 0 & \text{if } x \text{ is irrational} \end{cases}$$ Is $f$ continuous? Is $f$ continuous at any point of $\R^+$?}

\begin{solution}
 At any $x \in \Q$, setting $\epsilon = \frac{f(x)}{2}$, one can see that $0 \notin S_\epsilon(f(x))$. However, since irrationals are dense in the reals (basically the same assumption as the previous question), $S_\delta(x)$ contains irrational numbers $\forall \delta > 0$. Then $f(S_\delta(x))$ contains $0$, so it cannot be a subset of $S_\epsilon(f(x))$. Hence $f$ is not continuous for all rational $x$. \\
 However, $f$ is continuous at any irrational point. The proof will be described verbally, as it is cumbersome to construct the sets required, yet it adds nothing to what a verbal explanation provides. \\
 First, given that $\epsilon > 0$, we can find the finite number of natural numbers where $\frac{1}{n} \geq \epsilon$. For each of these natural numbers $n$, we can list all of the finitely many fractions with a natural number as numerator and $n$ as denominator. Repeat this for all $n$, and we have a finite set of fractions $A$. Let $a$ denote the distance between $x$ and the largest fraction in $A$ that is smaller than $x$. Let $b$ denote the distance between $x$ and the smallest fraction in $A$ that is greater than $x$. Finally, we can set $\delta =$ min$\{a,b\}$. Consider $y \in S_\delta(x)$, where $x$ is irrational. If $y$ is rational, it is not in $A$ (or else the distance between $x$ and $y$ is smaller that both $a$ and $b$, which is a contradiction). Therefore its denominator $q$ in lowest terms must be so great that $\frac{1}{q} < \epsilon$, so $f(y) \in S_\epsilon(0)$. Otherwise, $y$ is irrational, and $f(y) = 0 \in S_\epsilon(0)$. Therefore, we have proven that $f(S_\delta(x)) \subseteq S_\epsilon(0)$, which means that $f$ is continuous at irrational $x$.
\end{solution}

\subsection{Exercise 7.3}

\question{Consider a closed interval $[a,b]$ in the real line with $a$ and $b$ both finite, and $a < b$. Make this interval into a topological space by giving it the metric topology induced by the absolute value metric $d(x,y) = |x-y|$, as in Section 3. Prove that $[0,1], \cong [2,4]$. This shows that length is \textit{not} a topological property - it is not necessarily preserved by a homeomorphism.}

\begin{solution}
 $f(x) = 2x + 2$ is a homeomorphism between the spaces.
\end{solution}

\question{Consider the open unit interval $(0,1)$ as a topological space by giving it the metric topology induced by the absolute value metric $d(x,y) = |x-y|$ as in Section 3. Prove that $(0,1) \cong \R$. This shows again that length is not a topological property - it is not necessarily preserved by a homeomorphism. In fact, we have here an interval of finite length homeomorphic to one whose length is infinite!}

\begin{solution}
 $f(x) = \pi(x-0.5)$ is a homeomorphism.
\end{solution}

\question{Prove that the unit circle centered at the origin is homeomorphic to a square with unit perimeter centered at the origin.}

\begin{solution}
 \\We can use polar coordinates. Let the radius of the circle be $R$. For the square, given an angle $\theta$, draw a line in that direction, and let $s(\theta)$ be the supremum of all the lengths the line can take without exiting the square. Then
 $$f(r,\theta) = \left(r \times \frac{s(\theta)}{R}, \theta\right)$$
 is such a homeomorphism from the circle to the square. Using the same method, all convex polygons are homeomorphic with the circle, and hence each other.

\question{It was state in the introduction that a circle is not topologically the same as a straight line segment. The reason for this is not because the circle is curved and the line is not ("curveness" is not topological). Rather , it is because of the points of the line that are not end points.}

\begin{parts}
 
 \part{Let $[a,b]$ be a closed interval on the real line with $a$ and $b$ both finite and $a < b$ (so $[a,b]$ is a line segment). Convince yourself that the property of not being an end point is a topological property; in other words, if $h:[a,b] \rightarrow Y$ is a homeomorphism then $x \neq a$ and $x \neq b$, $h(x)$ cannot be an "end point" of Y.}
 
 
\begin{solution}
 \\Let $h(a) = p$, $h([a,b]) = Y'$. If there is an open set containing $p$ in $Y'$, intuitively, there should also be an open set that contains $a$ in $[a,b]$. Since this is false, intuition tells us that any open set around $p$ cannot be contained in $Y'$. This shouldn't be possible if $p$ is not an endpoint.
\end{solution}

\part{Convince yourself that a line segment and a circle are not homeomorphic.}

\begin{solution}
 \\If they are homeomorphic, a circle should then have two distinct end points. There doesn't seem to be any "intuitive" way to map a line segment continuously onto the circle while preserving two end points.
\end{solution}

\end{parts}

\question{We said in the discussion of Cartesian product (Section 3 of Chapter I) that $X$ is not a subset of $X \times Y$. However, $X$ is a "topological subset" of $X \times Y$ in the sense that $X$ is homeomorphic to a subset of $X \times Y$. Illustrate this case of $\R \times \R$ by convincing yourself that $\R$ is homeomorphic to the $x$-axis (= $\R \times \{0\}$) when the $x$-axis is given a topology as follows: a subset $U$ of the $x$-axis is open if and only if for each point $(x,0) \in U$, there is an $r > 0$ such tthat $S_r(x,0) \cap$ ($x$-axis) is contained in $U$. Is $\R$ homeomorphic to any other subset of $\R \times \R$ when that subset is topologized analogously?}

\begin{solution}
 \\This is very similar to our definition of open sets using the absolute value metric. Hence $f(x) = (x,0)$ is a homeomorphism. Similarly, $\R$ is homeomorphic the $y$-axis and any other straight line in $\R^2$.
\end{solution}

\subsection{Exercise 7.5}

\question{Show that for any point $p \in \R$, $\{p\}$ is a retract of $\R$.}

\begin{solution}
 $f(x) = p \forall x \in \R$ is a retraction of $\R$ onto $\{p\}$.
\end{solution}

\question{Show that $(0,1)$ is a retract of $\R$.}

\begin{solution}
 \\\underline{\textbf{I probably did something wrong here}} \\
 It seems that $(0,1)$ is not a retract (?) Proof: \\
 Assume such a function $r$ exists, and let $r(0) = a$. Since $a \in (0,1)$, we have $0 < a < 1$. Let $\epsilon = \frac{a}{2}$. $\forall \delta > 0$, let $b =$ min$\{\epsilon, \frac{\delta}{2}\}$. Note that $b > 0$. Then $b \in S_\delta(0)$, but $b \notin S_\epsilon(a)$. Since this is true $\forall \delta > 0$, $r$ is not continuous, which is a contradiction. \\
 If $(0,1)$ was a typo and the author meant $[0,1]$, then $$r(x) = \begin{cases} x & x \in [0,1] \\ 0 & x<0 \\ 1 & x > 1 \end{cases}$$ can be a retraction.
\end{solution}

\question{Show that $A \subseteq \R$ is a retract of $\R$ if and only if the identity function id$_A: A \rightarrow A$, defined by id$_A(a) = a$ for $a \in A$, can be \textit{extended} over $\R$ in the following sense. A function $f: A \rightarrow A$ can be \textit{extended} over $\R$ if there is a continuous function $F: \R \rightarrow \R$ such that $F(a) = f(a)$ for all $a \in A$.}

\begin{solution}
 If $A$ is a retract, $r$ is the required extension. If $F$ exists, it is a retraction.
\end{solution}

\question{Do you think that $\{0,1\}$ is a retract of $\R$? Why or why not?}

\begin{solution}
 \\Let $r(x) = 0$. Let $A = \{a \in \R|f(S_a(x)) = \{0\}\}$. If $A$ is empty, $r$ is not continuous at $x$ (let $\epsilon = 0.5$). Or else, $A$ must have a supremum , since $S_a(x)$ cannot contain 1. Then at least one of $S_\delta(x+a)$ or $S_\delta(x-a)$ must contain points which map to 0 and 1 $\forall \delta > 0$. Setting $\epsilon = 0.5$, $r$ cannot be continuous at both $x+a$ and $x-a$. Therefore, a retraction does not exists, and $\{0,1\}$ is not a retract.
\end{solution}
